API design for machine learning software: experiences from the scikit-learn project

### 2013-10-18 paper.tex
"stochastic gradient descent" in lowercase, not a brand name
minibatch SGD -> minibatch k-means
Shows that clustering benefits from partial_fit too.

Our implementation guidelines emphasize writing efficient but readable code.
In particular, we focus on making the codebase maintainable and
understandable in order to favor external contributions. Whenever practical,
algorithms implemented in \sklearn are written in Python,
using NumPy vector operations for numerical work.
This allows the code to remain concise, readable and efficient.
For critical algorithms that cannot be easily and efficiently
expressed as NumPy operations, we rely on Cython \citep{behnel2011cython}
to achieve competitive performance and scalability. Cython is a
compiled programming language that extends Python with static typing. It
produces efficient C extension modules that are importable from the
Python run-time system. Examples of Cython code in \sklearn are
Stochastic Gradient Descent for linear models, some clustering
algorithms, and decision trees.

@@

Finally, the Gensim topic modeling toolkit \citep{rehurek2010gensim}
exemplifies an API geared toward ``big data'' processing.
Gensim's method of dealing with large datasets is to use algorithms
that have small space complexity and can be updated online.
The API is designed around the Python concept of an ``iterable''
(supported in the language by a restricted form of co-routines called generators).
Some \sklearn estimators, notably Naïve Bayes and Stochastic Gradient Descent,
have a \texttt{partial\_fit} method to learn from a stream of samples
that is divided into mini-batches (chunks).
This way of processing, as argued in Section~\ref{sec:arrays},
allows for more efficient implementation.
We make no attempt to hide this batch-oriented processing from the user,
allowing control over the amount of memory dedicated to \sklearn algorithms.

>>>>

Our implementation guidelines emphasize writing efficient but readable code.
In particular, we focus on making the codebase maintainable and
understandable in order to favor external contributions. Whenever practical,
algorithms implemented in \sklearn are written in Python,
using NumPy vector operations for numerical work.
This allows the code to remain concise, readable and efficient.
For critical algorithms that cannot be easily and efficiently
expressed as NumPy operations, we rely on Cython \citep{behnel2011cython}
to achieve competitive performance and scalability. Cython is a
compiled programming language that extends Python with static typing. It
produces efficient C extension modules that are importable from the
Python run-time system. Examples of Cython code in \sklearn are
stochastic gradient descent for linear models, some clustering
algorithms, and decision trees.

@@

Finally, the Gensim topic modeling toolkit \citep{rehurek2010gensim}
exemplifies an API geared toward ``big data'' processing.
Gensim's method of dealing with large datasets is to use algorithms
that have small space complexity and can be updated online.
The API is designed around the Python concept of an ``iterable''
(supported in the language by a restricted form of co-routines called generators).
Some \sklearn estimators, among others the implementations of naïve Bayes
and minibatch $k$-means \citep{sculley2010web},
have a \texttt{partial\_fit} method to learn from a stream of samples
that is divided into mini-batches (chunks).
This way of processing, as argued in Section~\ref{sec:arrays},
allows for more efficient implementation.
We make no attempt to hide this batch-oriented processing from the user,
allowing control over the amount of memory dedicated to \sklearn algorithms.
